UGrade: Autograder for Competitive Programming Using Contestant PC as Worker

### 2019-07-01 src/paper.tex
fix contestant computers typ

\begin{abstract}
Competitive programming is a computer science competition where the contestants compete to solve computer science problems by writing a program which satisfies the problem constraints. Autograder is used to grade contestant solutions automatically in real-time. Usually, autograder is deployed in many computers to increase grading performance. In this research, contestant computers are used as a worker to run autograder. By using contestant computers as a worker, the number of workers will proportional to the number of contestant submissions, thus increasing grading performance. Every contestant computers have different specification and can affect grading fairness. To keep the fairness of the grading process, contestant's solution and jury's solution are executed in contestant's computer then compared to check whether contestant's solution satisfies the problem constraints. In order to evaluate the correctness of contestant's solution, the autograder uses input test-case to execute the contestant's solution and compares the output with the output test-case. Usually, the test-cases are some big text files generated by the problem setters. In this research, the test-case files are generated in the contestant computer using test-case generator program created by problem setter. In order to improve the security aspect, every contestant submission is graded multiple times. This research was tested by simulating grading process in contestant computers. The testing result indicates that using contestant computers as a worker gives performance improvement to the grading process. Further research is needed to improve the security aspect of this work. However, this research can be used to organize some competitive programming competition such as ACM-ICPC.
\end{abstract}

@@

In order to grade contestant submissions, online judge system has a subsystem called autograder. Contestant submissions which are source code in a certain programming language will be graded by the autograding system by compiling the program and executes compiled program using test-cases that have been prepared by juries or problem setter. According to \cite{jordanioi}, this grading method is called black-box grading. By using the autograding system, the grading process can be done automatically and juries do not have to evaluate contestant submissions manually. In order to increase the number of contestant submissions in a certain amount of time, juries usually deploy autograder in many computers. Fig. \ref{architecture-old} depicts the architecture of common online judge system. In order to run autograder in many computers, the juries need to prepare many computers with the same specification to keep the fairness of the grading process.

Currently, almost every competitive programming competition use online judge system to support the competition and use many computers to run autograder in order to improve grading performance. Every computer that runs autograder is called a worker. Grading performance is defined as the number of submissions graded in a certain amount of time. Even though autograder deployed in many computers, the grading performance often not enough to evaluate contestant solutions in real-time because the number of contestants is increasing. Furthermore, the number of computers to deploy autograder affect the procurement cost that juries need to be incurred. Therefore, a new grading system is needed to increase grading performance without increasing procurement cost that needs to be incurred.

When competing in a competitive programming competition, the contestants usually use their personal computer to write the solutions. Every contestant computers usually have sufficient specification to compile and execute contestant submissions. Therefore, contestant computers have the ability to run the autograder program and evaluate contestant submissions.

@@

There are some popular online judge systems that have been used to organize competitive programming competition. Some online judges offer other additional features like discussion forum, training gate, and rating system. Nowadays, most of the online judge deployed as a web application and use a specific computer to grade contestant submissions. There are many types of competitive programming competition rules. Most of the online judge only support a specific competition rule.

@@

Currently, most of the online judge use autograder to evaluate contestant submissions. According to \cite{danutamalms}, autograder is a system that compiles, executes and evaluate source code. Evaluates source code manually takes three minutes while using autograder only need ten seconds. By using autograder, contestants can receive grading feedback faster and reduce the work that needs to be done by juries. Basically, the autograder evaluate the source code by compiles the source code and executes the compiled program using predefined test-cases. The output of contestant's solution program compared to the predefined test-case and then graded. This evaluation method is called black-box grading \cite{jordanioi}.

@@

In competitive programming competition, every problem has time and memory constraints. Contestants are asked to solve the problem by writing a program that satisfies the constraints. According to ICPC rules, when contestant's solution exceeds the problem constraints, the solution is rejected and the contestant gets a time penalty. Thus, the autograding system needs to tell whether contestant's solution exceeds the constraints or not. The problem is, every computer has a different performance when executing a program. The same program might run faster in one computer and slower in another computer. Currently, most of the online judge system uses identical computers to evaluate contestant submissions. By using identical computers, the same program is expected to run at the same duration and consume the same amount of memories.

Contestant computers have different specification and performance. We cannot force the contestants to have an identical computer. Thus, we need a new time and memory measurement method. The performance of a computer is determined by its specifications such as CPU clock speed and operating system. We can tell the computer performance by its specifications. However, besides CPU clock speed and operating system, there are so many other factors that affect computer performance such as temperature, cache size, the program itself, and many other factors. Thus, determining computer performance by its specification is very hard and not feasible to do.

@@

The other way distribute grading jobs is by using push-based load balancing method. In push-based load balancing, the online judge server chooses the worker to do the grading jobs. By using this method, every contestant does not know which submission they grade, thus can increase system security. To improve system security, we can also grade every submission multiple times. In order to implement this method, we need the status of all workers. This method is pretty hard to implement because we need to poll the worker status periodically and choose the best worker to evaluate the contestant submissions.

@@

Because the autograder programs are deployed in the contestant computers, the contestants can do everything to the program. The contestant can attack the autograder program on their computer. There are many kinds of attacks that the contestant can do such as changing the compiler program, sending the false verdict to the server and refuse to grade other contestant submissions. In this work, we did not handle this kind of attacks, but there is a way to handle this kind of attacks.

@@

In this work, we named the autograder program as UGJob. UGJob asks UGServer for a job and does the grading process. UGJob uses UGSbox to compiles and executes the source code it receives from UGServer. We develop UGJob using Golang because of its ease of use. The UGJob is deployed in every contestant computers. Every installation of the UGJob is equipped with the same compiler to keep the fairness of the grading process.

>>>>

\begin{abstract}
Competitive programming is a computer science competition where the contestants compete to solve computer science problems by writing a program which satisfies the problem constraints. The autograder is used to grade contestant solutions automatically in real-time. Usually, autograder is deployed in many computers to increase grading performance. In this research, contestants' computers are used as a worker to run autograder. By using contestants' computers as a worker, the number of workers will proportional to the number of contestants' submissions, thus increasing grading performance. Every contestants' computers have different specification and can affect grading fairness. To keep the fairness of the grading process, contestant's solution and jury's solution are executed in contestant's computer then compared to check whether contestant's solution satisfies the problem constraints. In order to evaluate the correctness of contestant's solution, the autograder uses input test-case to execute the contestant's solution and compares the output with the output test-case. Usually, the test-cases are some big text files generated by the problem setters. In this research, the test-case files are generated in the contestant computer using test-case generator program created by problem setter. In order to improve the security aspect, every contestant submission is graded multiple times. This research was tested by simulating grading process in contestants' computers. The testing result indicates that using contestants' computers as a worker gives performance improvement to the grading process. Further research is needed to improve the security aspect of this work. However, this research can be used to organize some competitive programming competition such as ACM-ICPC.
\end{abstract}

@@

In order to grade contestants' submissions, online judge system has a subsystem called autograder. Contestants' submissions which are source code in a certain programming language will be graded by the autograding system by compiling the program and executes compiled program using test-cases that have been prepared by juries or problem setter. According to \cite{jordanioi}, this grading method is called black-box grading. By using the autograding system, the grading process can be done automatically and juries do not have to evaluate contestants' submissions manually. In order to increase the number of contestants' submissions in a certain amount of time, juries usually deploy autograder in many computers. Fig. \ref{architecture-old} depicts the architecture of common online judge system. In order to run autograder in many computers, the juries need to prepare many computers with the same specification to keep the fairness of the grading process.

Currently, almost every competitive programming competition uses online judge system to support the competition and use many computers to run autograder in order to improve grading performance. Every computer that runs autograder is called a worker. Grading performance is defined as the number of submissions graded in a certain amount of time. Even though autograder deployed in many computers, the grading performance often not enough to evaluate contestant solutions in real-time because the number of contestants is increasing. Furthermore, the number of computers to deploy autograder affect the procurement cost that juries need to be incurred. Therefore, a new grading system is needed to increase grading performance without increasing procurement cost that needs to be incurred.

When competing in a competitive programming competition, the contestants usually use their personal computer to write the solutions. Every contestants' computers usually have sufficient specification to compile and execute contestants' submissions. Therefore, contestants' computers have the ability to run the autograder program and evaluate contestants' submissions.

@@

There are some popular online judge systems that have been used to organize competitive programming competition. Some online judges offer other additional features like discussion forum, training gate, and rating system. Nowadays, most of the online judges are deployed as a web application and use a specific computer to grade contestants' submissions. There are many types of competitive programming competition rules. Most of the online judges only support a specific competition rule.

@@

Currently, most of the online judges use autograder to evaluate contestants' submissions. According to \cite{danutamalms}, autograder is a system that compiles, executes and evaluate source code. Evaluates source code manually takes three minutes while using autograder only need ten seconds. By using autograder, contestants can receive grading feedback faster and reduce the work that needs to be done by juries. Basically, the autograder evaluate the source code by compiles the source code and executes the compiled program using predefined test-cases. The output of contestant's solution program compared to the predefined test-case and then graded. This evaluation method is called black-box grading \cite{jordanioi}.

@@

In competitive programming competition, every problem has time and memory constraints. Contestants are asked to solve the problem by writing a program that satisfies the constraints. According to ICPC rules, when contestant's solution exceeds the problem constraints, the solution is rejected and the contestant gets a time penalty. Thus, the autograding system needs to tell whether contestant's solution exceeds the constraints or not. The problem is, every computer has a different performance when executing a program. The same program might run faster in one computer and slower in another computer. Currently, most of the online judge system uses identical computers to evaluate contestants' submissions. By using identical computers, the same program is expected to run at the same duration and consume the same amount of memories.

Contestants' computers have different specification and performance. We cannot force the contestants to have an identical computer. Thus, we need a new time and memory measurement method. The performance of a computer is determined by its specifications such as CPU clock speed and operating system. We can tell the computer performance by its specifications. However, besides CPU clock speed and operating system, there are so many other factors that affect computer performance such as temperature, cache size, the program itself, and many other factors. Thus, determining computer performance by its specification is very hard and not feasible to do.

@@

The other way distribute grading jobs is by using push-based load balancing method. In push-based load balancing, the online judge server chooses the worker to do the grading jobs. By using this method, every contestant does not know which submission they grade, thus can increase system security. To improve system security, we can also grade every submission multiple times. In order to implement this method, we need the status of all workers. This method is pretty hard to implement because we need to poll the worker status periodically and choose the best worker to evaluate the contestants' submissions.

@@

Because the autograder programs are deployed in the contestants' computers, the contestants can do everything to the program. The contestant can attack the autograder program on their computer. There are many kinds of attacks that the contestant can do such as changing the compiler program, sending the false verdict to the server and refuse to grade other contestants' submissions. In this work, we did not handle this kind of attacks, but there is a way to handle this kind of attacks.

@@

In this work, we named the autograder program as UGJob. UGJob asks UGServer for a job and does the grading process. UGJob uses UGSbox to compiles and executes the source code it receives from UGServer. We develop UGJob using Golang because of its ease of use. The UGJob is deployed in every contestants' computers. Every installation of the UGJob is equipped with the same compiler to keep the fairness of the grading process.
